---
title: "Eades Exam 3"
author: "Joshua Eades"
date: "11/30/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(janitor)
library(broom)
FS <- read_csv("./../Data/FacultySalaries_1995.csv")
df3 <- read_csv("./../Data/Juniper_Oils.csv")
Full <- FS %>% select(c(1:4,9:17),contains("AvgFull")) %>% 
  pivot_longer(ends_with("FullProfSalary"),
               names_to="Rank",values_to="Salary",
               names_prefix="AvgFull") %>% 
  mutate(ProfType="Full")

Associate <- FS %>% select(c(1:4,9:17),contains("AvgAssoc")) %>% 
  pivot_longer(ends_with("AssocProfSalary"),
               names_to="Rank",values_to="Salary",
               names_prefix="AvgAssoc") %>% 
  mutate(ProfType="Associate")

Assistant <- FS %>% select(c(1:4,9:17),contains("AvgAssist")) %>% 
  pivot_longer(ends_with("AssistProfSalary"),
               names_to="Rank",values_to="Salary",
               names_prefix="AvgAssist") %>% 
  mutate(ProfType="Assistant")

All <- FS %>% select(c(1:4,9:17),contains(c("All"))) %>% 
  pivot_longer(cols = ends_with("ryAll"),
               names_to="Rank",values_to="Salary",
               names_prefix="AvgProf") %>% 
  mutate(ProfType="All")

full2 <- rbind(Full,Associate,Assistant,All)
```

### Numbers 1 and 2
After loading the "FacultySalaries_1995.csv" file, I cleaned the data frame and saved it as a new data frame called "full2". 

```{r,echo=FALSE,message=FALSE}
full3 <- rbind(Full,Associate,Assistant)
full4 <- full3 %>% filter(Tier==c("I","IIA","IIB"))
p1<- ggplot(full4, aes(x=ProfType,y=Salary,fill=ProfType)) +
  geom_boxplot() +
  facet_wrap(~Tier) +
  theme_minimal() +
  labs(x="Rank",fill="Rank")
p1
```

The above figure is facet wrapped by tier of university and shows Salary dependent on Type of Faculty. I could not figure out how to include some of the non-finite values.

```{r,echo=FALSE, message=FALSE}
mod1 <- aov(data = full2,
            formula = Salary ~ State + Tier + Rank)

summary(mod1)
```

Above, we see the interaction of State, Tier, and Rank on Salary. Each, individually, has a significant influence on the salary of these employees. This table is saved as a file in this directory as "Salary_ANOVA_Summary.txt". 

### Numbers 3 and 4

First, I input the "Juniper_Oils.csv" file into my report as "df3". I cleaned up the data frame and saved is as a new data frame called "df4".

```{r,include=FALSE}
df3 <- read_csv("./../Data/Juniper_Oils.csv")

df4 <-df3 %>% 
  pivot_longer(contains(c("alpha-pinene","para-cymene","alpha-terpineol",
  "cedr-9-ene","alpha-cedrene","beta-cedrene","cis-thujopsene","alpha-himachalene",
  "beta-chamigrene","cuparene","compound 1","alpha-chamigrene","widdrol","cedrol",
  "beta-acorenol","alpha-acorenol","gamma-eudesmol","beta-eudesmol","alpha-eudesmol",
  "cedr-8-en-13-ol","cedr-8-en-15-ol","compound 2","thujopsenal")),
  names_to="Chemical_ID",
  values_to="Concentration")
```

Below is a figure of the graph "Concentration vs YearsSinceBurn". 

```{r,echo=FALSE,message=FALSE}
fig2 <- ggplot(df4,aes(x=YearsSinceBurn,y=Concentration)) +
  geom_smooth() +
  facet_wrap(~Chemical_ID,scales = "free_y") +
  theme_minimal()
fig2
```

What this shows us is the impact that the years since the time of the burn has on the concentration of these chemicals.

### Number 5

```{r,echo=FALSE,message=FALSE}
mod2 <- glm(data = df4,
            formula = Concentration ~ Chemical_ID + YearsSinceBurn)

mod2t <- mod2 %>% tidy()
mod2t
```

Above, we see a tidied version of the glm model with the formula: Concentration ~ Chemical_ID + YearsSinceBurn. When tidied, it still contained p-values > .05 and I was not sure how to change this. We are still seeing those chemical concentrations that are most influenced by YearsSinceBurn.